Adaptive broadcast tree for multicores

### 2013-06-10 paper.tex
Added the UMP breakdown of ziger1 to the paper

\paragraph{Atomic broadcast} \stefan{Explain the guarantees provided
  by atomic broadcasts}. Atomic broadcasts are frequently used to
implement higher-level distributed algorithms on top of it: examples
are replication such as state machine replication. As a first step, we
evaluate the performance of sending one message as a broadcast to all
nodes. Broadcasts are one of the most important communication
operations for parallel applications~\cite{Bruck1992} \stefan{Database
  joins}.

@@

>>>>

\paragraph{Atomic broadcast} An Atomic broadcasts is a broadcast
messaging protocol that is reliable in the sense that if a message is
received by one of the participating nodes, it is also received by all
other nodes. Furthermore, the order of messages as seen by all
participants is the same. Atomic broadcasts are frequently used to
implement higher-level distributed algorithms on top of it: examples
are replication such as state machine replication. As a first step, we
evaluate the performance of sending one message as a broadcast to all
nodes. Broadcasts are one of the most important communication
operations for parallel applications~\cite{Bruck1992}. \stefan{Database
  joins}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{appendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{UMP performance}

\input{graphs/ziger_ump_breakdown}
